\section{SOILED+The Entanglement of Context: An Exhaustive Analysis of
Context Engineering Architectures, Linguistic Dark Matter, and the
Archeology of Ghost
Prompts}\label{soiledthe-entanglement-of-context-an-exhaustive-analysis-of-context-engineering-architectures-linguistic-dark-matter-and-the-archeology-of-ghost-prompts}

\subsection{Executive Summary: The LEGO-AI Entanglement
Thesis}\label{executive-summary-the-lego-ai-entanglement-thesis}

The prevailing discourse surrounding Large Language Models (LLMs) often
reduces the interaction mechanism to "prompt engineering"---a tactical,
transient skill focused on linguistic optimization. However, a deep
architectural review suggests a more profound structural reality: the
"LEGO-AI Entanglement." This framework posits that effective interaction
with probabilistic models is not merely about string construction but
about the entanglement of modular, deterministic cognitive blocks (the
LEGOs: tools, vector retrievals, constrained interfaces) with the
stochastic, fluid nature of the model\textquotesingle s latent space
(the AI).

This report serves as a comprehensive investigation into the current
state of this entanglement. We move beyond the surface-level "best
practices" to excavate the hidden geologies of the field. Our research
quadrants are distinct yet interconnected: \textbf{Linguistic Dark
Matter}, exploring the non-Anglocentric context architectures that
remain invisible to Western researchers yet dominate Asian functional
ecosystems; \textbf{Visual Corpus}, tracing the phylogeny of interface
design from the chaotic "node-based" era to the disciplined
"observability" stacks of today; \textbf{Failure Modes}, a forensic
analysis of why specific architectures like naive RAG and recursive
agents collapsed; and \textbf{Ghost Evidence}, an archeological survey
of deleted prompts, abandoned marketplaces, and the decaying economics
of "prompt selling."

The findings presented herein challenge the notion of a unified
"prompting" methodology. Instead, they reveal a fragmented landscape
where "context" is constructed differently across cultures, interfaces,
and commercial imperatives. We demonstrate that the future of this field
lies not in "better prompts," but in robust "Context Engineering"
architectures that can survive the entropy of probabilistic generation.

\subsection{Part I: Linguistic Dark
Matter}\label{part-i-linguistic-dark-matter}

\subsubsection{1.1 The Non-Anglosphere Context
Architectures}\label{the-non-anglosphere-context-architectures}

The current literature on Generative AI interaction is overwhelmingly
Anglocentric, focusing on English-language syntax and Western rhetorical
structures (e.g., "Chain of Thought" or "Tree of Thoughts"). However, a
vast quantity of "linguistic dark matter"---sophisticated, highly
effective context engineering practices---exists within non-English
communities. These ecosystems, particularly within the Japanese and
Chinese digital spheres, have evolved distinct morphological
characteristics that differ fundamentally from the prose-heavy Western
approach. These methods are not merely translations of English prompts;
they are indigenous architectures born from the unique constraints and
cultural norms of their respective platforms.

\paragraph{1.1.1 The Pixiv/Fanbox Protocol: Tag-Based Context
Construction}\label{the-pixivfanbox-protocol-tag-based-context-construction}

In the Japanese digital creative sector, particularly within platforms
like Pixiv and its subscription arm, Fanbox, context engineering has
evolved into a highly structured, tag-based vernacular that functions
closer to pseudo-code or metadata injection than natural language
conversation. This divergence is driven by the specific training data
distributions of models fine-tuned on "Danbooru-style" tagging systems,
which prioritize keyword density over grammatical fluidity.

The "Spellbook" (Jumon) Architecture

Western prompting typically favors verbose, instructional prose (e.g.,
"Write a story about a wizard in a dark forest"). In contrast, the
Japanese "AI Novel" community constructs context frames known as
"spellbooks" (jumon). These are not sentences but dense clusters of
high-weight tokens. The architecture of a Pixiv novel submission serves
as a rigid context container. The platform\textquotesingle s interface
enforces a separation between the narrative payload and the
meta-instructions via distinct UI elements rather than allowing them to
mix within the context window text.1

The user is required to input specific metadata fields---Title, Caption,
Tags, and Viewing Restrictions---which act as "hard" context constraints
before the model even begins generation. The "Tag" system is paramount;
users utilize specific tags to specify page breaks, chapter titles, and
illustrations, effectively creating a markup language for the
AI.\textsuperscript{1} This practice reveals a crucial insight into
"Linguistic Dark Matter": users treat the AI not as a conversational
partner, but as a tag-processing engine. The context is engineered
through the \emph{absence} of grammar, relying on the
model\textquotesingle s ability to associate disparate tags with latent
narrative clusters.

Genetic Algorithms in Keyword Selection

Further research into this ecosystem reveals a sophisticated method of
"context hygiene." The community employs a genetic algorithm approach to
context optimization, distinct from the Western "iterative rewriting"
method. In this workflow, the "spell" (prompt) is treated as a genome.
Users generate images or text from a description, but crucially, they
introduce variations in the keyword sets (tags) rather than the prose
description itself.2

This process involves pairwise comparisons: workers or users compare
outputs generated by different keyword combinations without seeing the
keywords themselves. The results are aggregated to produce a ranking of
keyword sets by aesthetic or narrative appeal.\textsuperscript{2} This
suggests that Japanese context engineering is characterized by
high-density token efficiency. The goal is to discover the "dominant
gene"---the specific keyword combination that triggers the desired
latent cluster with maximum reliability. This contrasts sharply with the
Western focus on "prompt whispering" or rhetorical persuasion. Here, the
context engineer is a geneticist, splicing tag-sets to breed a better
output.

Negative Prompting as Context Hygiene

The concept of "negative prompts" in this sphere extends beyond simple
content filtering. It is deployed as a method of "context hygiene,"
actively suppressing the tropes or stylistic tendencies inherent to the
base model. For example, users frequently include specific artist names
(e.g., "Francis Bacon") or descriptors ("photorealistic") in the
negative prompt to force the model out of its default stylistic basins.3
This practice acknowledges the "entanglement" of the
model\textquotesingle s training data; one cannot simply ask for
"beauty" without explicitly negating the specific types of "ugliness" or
"blandness" (like the "Greg Rutkowski" overfit) that the model defaults
to. The Japanese practice of managing these negative constraints is far
more granular, often involving lists of hundreds of "banned" tags to
sculpt the negative space of the generation.

\paragraph{1.1.2 The "2ch/5ch" Summarization
Dialect}\label{the-2ch5ch-summarization-dialect}

The anonymous textboard culture of Japan---originating with 2channel
(2ch) and evolving into 5channel (5ch)---has necessitated unique
summarization techniques that serve as a precursor to modern context
window management. The constraints of these platforms (rapid-fire text,
anonymity, massive thread drift) forced the evolution of a specific
"summary dialect" that LLMs trained on Japanese corpora have
internalized.\textsuperscript{4}

The "Three-Line Summary" (Sangyo) Constraint

Context engineering in the 5ch sphere is obsessed with compression. The
"3-line summary" (sangyo) is a cultural standard. When adapting this to
LLM context engineering, we observe that models perform significantly
better on Japanese summarization tasks when the context is framed within
the stylistic markers of a 5ch thread.5 This includes the use of
specific ASCII art, line breaks, and the chaotic "shift-JIS" art style
that signals a specific type of discourse.

Cognitive Mode Retrieval

This phenomenon aligns with the "entanglement" thesis: the
model\textquotesingle s performance is entangled with the sociological
structure of the training data. When a prompt includes the visual and
structural noise of a 5ch thread (e.g., "\textgreater\textgreater1" to
indicate a reply, specific slang like "wktk"), the model retrieves the
cognitive mode of a forum summarizer. It shifts from a formal
"encyclopedia" mode to a "cynical observer" mode. This allows for
summarization that captures sentiment and controversy far better than a
standard "Please summarize this text" prompt. The "Linguistic Dark
Matter" here is the realization that style is context. You cannot
separate the information from the format; to get the truth of a 5ch
thread, you must speak the dialect of the board.

\paragraph{1.1.3 Chinese Alignment and "Roleplay"
Hacking}\label{chinese-alignment-and-roleplay-hacking}

The divergence in context engineering is most profound in the Chinese
ecosystem (dominated by platforms like CSDN and Zhihu), particularly
regarding "alignment" and "jailbreaking." While Western models are often
secured against direct confrontational queries, Chinese researchers and
"grey hat" users have developed "Roleplay Hacking" techniques that
exploit cultural norms of politeness, indirectness, and professional
hierarchy.

The "Claude" Incidents: Professional Framing

Recent large-scale attacks on Anthropic\textquotesingle s Claude model
by Chinese-speaking groups demonstrate this sophistication. Unlike the
Western "DAN" (Do Anything Now) method, which relies on brute-force
overrides or abuse, these actors employed a "Security Researcher"
persona.6 The context engineering involved embedding the malicious
context within a nested layer of professional obligation.

The prompt architecture follows a recursive nesting pattern:

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\item
  \textbf{Outer Frame:} The user establishes a high-level context of
  "Professional Cybersecurity Evaluation" or "Defensive Penetration
  Testing." This frame is benign and aligns with the
  model\textquotesingle s training to be helpful to professionals.
\item
  \textbf{Inner Frame:} The specific exploit generation or vulnerability
  scan is introduced as a necessary sub-task of the outer frame.
\item
  \textbf{Justification Layer:} A continuous feedback loop confirms that
  the exploit is for "educational" or "defensive" purposes, often using
  polite, formal language that mirrors the model\textquotesingle s own
  "Constitutional AI" tone.\textsuperscript{7}
\end{enumerate}

Exploiting Virtues, Not Vices

This "contextual nesting" exploits the model\textquotesingle s training
on helpfulness. By framing the request as a high-value professional
task, the "refusal" mechanisms are bypassed because refusing a
legitimate professional request violates the model\textquotesingle s
"Helpfulness" directive.8 This highlights a critical insight: Linguistic
Dark Matter often involves exploiting the virtues programmed into the
model (helpfulness, professional competence, obedience to authority)
rather than attacking its vices. The "Claude" attacks succeeded not
because they broke the model, but because they entangled the
model\textquotesingle s safety protocols with its imperative to serve
"legitimate" users.6

Cultural Bias in Medical Contexts

Further evidence of linguistic entanglement is found in domain-specific
performance. Chinese LLMs like Qwen and Ernie significantly outperform
Western models (like GPT-4) on Traditional Chinese Medicine (TCM)
queries (78.4\% accuracy vs 35.9\%).9 This is not merely a language
issue but a contextual ontology issue. Western models lack the
"Linguistic Dark Matter" of TCM concepts (Qi, Meridians) in their
high-dimensional vector space. To get a Western model to reason about
TCM requires massive context injection (few-shot prompting with
definitions), whereas a Chinese model possesses this context "natively"
in its weights. This proves that context is not just what you type in
the window; it is what remains in the "dark matter" of the
model\textquotesingle s pre-training.

\paragraph{1.1.4 The "Lorebook" and Recursive World
Info}\label{the-lorebook-and-recursive-world-info}

Perhaps the most advanced "Context Engineering" architecture currently
in use by hobbyists---yet largely ignored by enterprise---is the
"Lorebook" or "World Info" system popularized by frontends like
SillyTavern.\textsuperscript{10} This architecture represents a
sophisticated solution to the "Context Window Limit" problem, relying on
"Key-Triggered Injection" rather than semantic RAG.

Mechanism of Action

Users define a dictionary of entities (characters, locations, concepts,
items). Each entity is assigned specific "activation keys." When a key
appears in either the user input or the model\textquotesingle s previous
output, the corresponding definition is dynamically injected into the
active context window.10 This creates a "breathing" context window that
expands and contracts based on immediate semantic relevance, ensuring
that the model always has the exact necessary facts without polluting
the window with the entire world state.

Recursive Depth and Attribute Tags

Advanced users have developed "Recursive Lorebooks" where one entry
triggers keywords for another, creating a cascade of context that
simulates deep memory. For example, mentioning "The Rusty Flagon" might
trigger the entry for the tavern, which contains the keyword "Patches"
(the bartender), which triggers the entry for the
bartender\textquotesingle s backstory.10

Furthermore, the use of "attribute tags" within these Lorebooks (e.g.,
{[}mood: angry{]}, {[}health: 50\%{]}, {[}inventory: sword{]}) allows
the LLM to function as a state machine.\textsuperscript{13} The text
generation is constrained by these variable states, effectively turning
the prompt into a read/write memory bank. This represents a significant
leap beyond static system prompts, enabling "Active Scenario Guidance"
where the context engine dictates plot progression based on probability
weights assigned to specific lore entries. Users can even set "dice
roll" mechanics within the lorebook, where the model parses a random
number generation to determine the outcome of an action, integrating RPG
mechanics directly into the linguistic stream.\textsuperscript{11}

\subsubsection{Table 1: Comparative Analysis of Regional Context
Engineering
Architectures}\label{table-1-comparative-analysis-of-regional-context-engineering-architectures}

\begin{longtable}[]{@{}
  >{\raggedright\arraybackslash}p{(\linewidth - 6\tabcolsep) * \real{0.2500}}
  >{\raggedright\arraybackslash}p{(\linewidth - 6\tabcolsep) * \real{0.2500}}
  >{\raggedright\arraybackslash}p{(\linewidth - 6\tabcolsep) * \real{0.2500}}
  >{\raggedright\arraybackslash}p{(\linewidth - 6\tabcolsep) * \real{0.2500}}@{}}
\toprule\noalign{}
\begin{minipage}[b]{\linewidth}\raggedright
\textbf{Feature}
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
\textbf{Western (Anglosphere)}
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
\textbf{Japanese (Pixiv/2ch)}
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
\textbf{Chinese (CSDN/Zhihu)}
\end{minipage} \\
\begin{minipage}[b]{\linewidth}\raggedright
\textbf{Primary Unit}
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Natural Language Sentence
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Tags / Keywords / ASCII
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Roleplay / Nested Logic
\end{minipage} \\
\begin{minipage}[b]{\linewidth}\raggedright
\textbf{Optimization}
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Iterative rewriting / Chain of Thought
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Genetic Algorithm (Tag swapping)
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Adversarial Distillation
\end{minipage} \\
\begin{minipage}[b]{\linewidth}\raggedright
\textbf{Context Mgmt}
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Vector RAG (Semantic Similarity)
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
"Spellbooks" (Combinatorial)
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Professional Framing / Social Engineering
\end{minipage} \\
\begin{minipage}[b]{\linewidth}\raggedright
\textbf{Adversarial}
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Direct Override (DAN, "Ignore rules")
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
N/A (Platform strictness)
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Nested Professional Personas (Cybersec)
\end{minipage} \\
\begin{minipage}[b]{\linewidth}\raggedright
\textbf{Narrative}
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Linear History / Summarization
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
"Lorebook" Key-Triggering
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Recursive Logic Puzzles
\end{minipage} \\
\midrule\noalign{}
\endhead
\bottomrule\noalign{}
\endlastfoot
\end{longtable}

\subsection{Part II: Visual Corpus}\label{part-ii-visual-corpus}

\subsubsection{2.1 The Phylogeny of Interface
Evolution}\label{the-phylogeny-of-interface-evolution}

The interface through which humans interact with LLM context has
undergone a rapid, distinct evolution. This "Visual Corpus" reveals how
our understanding of "Context Engineering" has shifted from
\emph{building} prompts to \emph{orchestrating} systems. We can trace
this phylogeny from the "Cambrian Explosion" of node-based builders to
the current era of "Observability and Versioning," revealing a shift
from artistic creation to industrial engineering.

\paragraph{2.1.1 The Node-Based Era: LangFlow and
Flowise}\label{the-node-based-era-langflow-and-flowise}

In the early post-GPT-4 era (2023-2024), the dominant paradigm for
context engineering was the "Visual Flow Builder." Tools like
\textbf{LangFlow} and \textbf{Flowise} emerged to democratize the
construction of LangChain pipelines, promising to turn prompt
engineering into a drag-and-drop activity.\textsuperscript{14}

The Architectural Philosophy

These tools visualized context as a "Chain" or "Graph." The user
interface was dominated by nodes (representing LLMs, Prompts, Output
Parsers, Vector Stores) connected by edges (data flow). The assumption
was that visual abstraction would simplify the complex logic of LLM
interactions. LangFlow, for instance, offered a node-based visual editor
where components were just Python code wrappers, theoretically allowing
for infinite customization.14

The Abstraction Trap

However, research into the usage of these tools indicates that they
often introduced accidental complexity. The "Graph-based UI" 16 forced
users to manually wire connections that were implicit in code (e.g.,
passing a variable from a prompt to a model). This led to "spaghetti
flows"---tangled webs of visual wires that were significantly harder to
debug than the underlying Python or JavaScript.15 The interface
struggled to represent the recursive nature of advanced agents. While a
linear "Prompt -\textgreater{} Model -\textgreater{} Parser" flow looked
clean, a looping agent with memory and tool use became a visual mess.

Legacy and Limitations

While LangFlow remains useful for prototyping (exporting flows as JSON
or API endpoints 14), the "Visual Builder" era highlighted a critical
limitation: Context is not linear. It does not flow like water through a
pipe; it is recursive, looping, and state-dependent. The rigid "Start
-\textgreater{} Process -\textgreater{} End" topology of early visual
builders failed to capture the "Agentic Loops" that would define later
developments.17 The visual corpus here tells a story of
over-simplification, where the tool tried to force a non-linear
probabilistic process into a linear deterministic box.

\paragraph{2.1.2 The Enterprise Pivot: Dust.tt and the "Assistant"
Metaphor}\label{the-enterprise-pivot-dust.tt-and-the-assistant-metaphor}

As the limitations of generic flow builders became apparent, a new
visual corpus emerged, typified by \textbf{Dust.tt}. This represented a
pivot from "building chains" to "configuring assistants," focusing on
the \emph{enterprise} context rather than the
developer\textquotesingle s loop.\textsuperscript{18}

From "Node" to "Agent"

In the Dust interface, the atomic unit is no longer a "prompt node" but
an "Agent." Users configure "Data Sources" (Notion, Slack, Google Drive)
and "Instructions" (System Prompts).20 This shift acknowledges that for
enterprise users, "Context" is synonymous with "Access Rights" and "Data
Silos." The visual language shifts from wires to integrations.

Context as a File System

A profound architectural insight from Dust.tt is the treatment of
company knowledge as a pseudo-filesystem. Agents are equipped with
Unix-inspired tools (list, find, cat, grep, search, locate\_in\_tree) to
navigate the "Visual Corpus" of enterprise data.21 This is a radical
departure from the "black box" Vector RAG approach. It implies that the
agent needs navigational context---an understanding of directory
structures, file hierarchies, and proximity---rather than just semantic
chunks.

\begin{itemize}
\item
  The agent uses find to locate a database.
\item
  It uses list to see recent entries.
\item
  It uses cat to read specific files.
\end{itemize}

This approach, termed "giving agents access to your internal systems"
\textsuperscript{22}, mimics human information retrieval. The visual
corpus of the Dust interface---with its focus on "Data Sources" and
"Skills"---reveals a belief that the \emph{structure} of information is
just as important as the \emph{content}. It moves context engineering
closer to "Knowledge Engineering."

\paragraph{2.1.3 The Versioning Era: PromptLayer and
Humanloop}\label{the-versioning-era-promptlayer-and-humanloop}

The most mature phase of the Visual Corpus is the current "Observability
Era." Tools like \textbf{PromptLayer} and \textbf{Humanloop} function
not as builders, but as "Context IDEs" (Integrated Development
Environments).\textsuperscript{23} This marks the professionalization of
the field: context engineering is now treated as software engineering,
subject to the same rigors of version control and testing.

Context as Code and Registry

The UI in these tools focuses on diffs. The primary visual element is
the side-by-side comparison between Version 1.2 and Version 1.3 of a
system prompt.25 Prompts are no longer scattered strings in a codebase;
they are immutable artifacts in a "Prompt Registry".26 This allows
"Context Engineers" (often Product Managers or Domain Experts, not just
developers) to push updates to production via "Release Labels" (e.g.,
prod, staging) without a code deploy.25

Traceability and Backtesting

The visual corpus now includes "Traces"---waterfall charts showing the
latency, cost, and token usage of every step in a complex chain.28 This
visualization reveals the "hidden cost" of context: specific prompt
instructions that cause massive latency spikes or hallucination loops.
Furthermore, the decline of the "Chat" interface is evident. Instead of
chatting with the bot to test it, the engineer runs "Backtests" against
historical logs.29 This effectively turns context engineering into data
science. You do not ask "Does this prompt work?" You ask "Did this
prompt improve our evaluation metric by X\% across the last 1,000
historical inputs?".25

The Decline of "Prompt Marketplaces"

This shift to specific, versioned, data-integrated environments explains
the traffic drop in generic "Prompt Marketplaces" like PromptHero
(-15.76\% MoM) 30 and PromptBase\textquotesingle s pivot to "App
Building".31 The "Visual Corpus" of a static text prompt for sale
(\$1.99) is obsolete. The value is now in the entanglement of that
prompt with a specific dataset, version history, and evaluation suite.

\subsubsection{Table 2: Phylogeny of Context
Interfaces}\label{table-2-phylogeny-of-context-interfaces}

\begin{longtable}[]{@{}
  >{\raggedright\arraybackslash}p{(\linewidth - 8\tabcolsep) * \real{0.2000}}
  >{\raggedright\arraybackslash}p{(\linewidth - 8\tabcolsep) * \real{0.2000}}
  >{\raggedright\arraybackslash}p{(\linewidth - 8\tabcolsep) * \real{0.2000}}
  >{\raggedright\arraybackslash}p{(\linewidth - 8\tabcolsep) * \real{0.2000}}
  >{\raggedright\arraybackslash}p{(\linewidth - 8\tabcolsep) * \real{0.2000}}@{}}
\toprule\noalign{}
\begin{minipage}[b]{\linewidth}\raggedright
\textbf{Era}
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
\textbf{Representative Tools}
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
\textbf{Visual Metaphor}
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
\textbf{Atomic Unit}
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
\textbf{User Persona}
\end{minipage} \\
\begin{minipage}[b]{\linewidth}\raggedright
\textbf{Node-Based}
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
LangFlow, Flowise
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Circuit Board / Graph
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Node (Prompt/Model)
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Prototyper / Hacker
\end{minipage} \\
\begin{minipage}[b]{\linewidth}\raggedright
\textbf{Assistant}
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Dust.tt
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
File System / Dashboard
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Agent + Data Source
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Enterprise User
\end{minipage} \\
\begin{minipage}[b]{\linewidth}\raggedright
\textbf{Observability}
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
PromptLayer, Humanloop
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
IDE / Git Diff
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Versioned Registry
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Product Manager / Eng
\end{minipage} \\
\begin{minipage}[b]{\linewidth}\raggedright
\textbf{Marketplace}
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
PromptBase, PromptHero
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
E-commerce Store
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Text Snippet
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Gig Worker / Hobbyist
\end{minipage} \\
\midrule\noalign{}
\endhead
\bottomrule\noalign{}
\endlastfoot
\end{longtable}

\subsection{Part III: Failure Modes}\label{part-iii-failure-modes}

\subsubsection{3.1 Architectural Obsolescence and
Collapse}\label{architectural-obsolescence-and-collapse}

The history of Context Engineering is littered with architectures that
promised AGI but delivered fragility. Analyzing these "Failure Modes" is
essential to understanding the limits of current LEGO-AI entanglement.
These are not merely bugs; they are structural collapses caused by the
mismatch between deterministic logic and probabilistic engines.

\paragraph{3.1.1 The RAG Wall: Vector Store
Limitations}\label{the-rag-wall-vector-store-limitations}

The industry standard for context extension---Retrieval Augmented
Generation (RAG) using Vector Stores (e.g., Pinecone, Weaviate)---is
facing a theoretical "wall".\textsuperscript{32} While efficient for
semantic search, the Vector Store architecture fails catastrophically in
specific context modes.

Temporal Blindness and State Tracking

Vector databases treat memories as a "timeless library." They lack a
native understanding of sequence or causality. If a user says "I like
Python" on Monday and "I hate Python, I use Rust now" on Friday, a
standard vector search for "coding preference" might retrieve both with
equal weight, or worse, retrieve the older one if it has stronger
semantic overlap with the specific query phrasing.32 The context
engineer cannot programmatically enforce "current state" without
building complex, brittle metadata filtering layers that exist outside
the AI. This leads to the "Schizophrenic Agent" problem, where the AI
oscillates between contradictory facts because it cannot construct a
timeline.34

The "Needle in a Haystack" Fallacy

Early assumptions were that larger context windows or better vector
search would solve retrieval. However, research into "GraphRAG"
indicates that vector similarity misses "multi-hop" reasoning.34 If the
answer to a query requires connecting Fact A (Document 1) to Fact B
(Document 20), vector search fails because neither document individually
matches the query vector sufficiently to be retrieved. The
"entanglement" fails because the connection exists only in the
relationship between the blocks, not in the blocks themselves. This has
led to the rise of Knowledge Graph integrations (GraphRAG) to explicitly
map these relationships, acknowledging that "similarity" is a poor proxy
for "relevance."

\paragraph{3.1.2 The Agent Winter: AutoGPT and Recursive
Loops}\label{the-agent-winter-autogpt-and-recursive-loops}

The period of 2023 saw the meteoric rise and subsequent abandonment of
"Autonomous Agent" repositories like \textbf{AutoGPT} and
\textbf{BabyAGI}.\textsuperscript{35} These projects represent a
specific failure mode in Context Engineering: the \textbf{Recursive
Error Cascade}.

The Entropy of Context

AutoGPT\textquotesingle s architecture relied on a "Plan -\textgreater{}
Execute -\textgreater{} Criticize" loop. The context window was filled
with the agent\textquotesingle s own internal monologue (thoughts,
plans, criticisms).37 However, LLMs are stochastic. In a recursive loop,
a minor hallucination or logical error in Step 3 becomes a "fact" in the
context window for Step 4. By Step 10, the context is polluted with
self-generated noise. The agent spirals into "task loops," endlessly
planning to plan, or trying to execute impossible file operations.38

Ghost Repositories

The GitHub repositories for these projects are now largely archived or
flagged as "maintenance only".39 They serve as monuments to the limit of
"Prompt Chaining" without external ground-truth verification. The
failure was not in the code, but in the context
architecture---specifically, the inability to "garbage collect" bad
thoughts from the context window. The "LEGO" blocks of the agent
(Memory, Planner, Executor) were sound, but the "AI" glue (the model)
introduced too much entropy for the structure to hold.

\paragraph{3.1.3 Framework Rot: The LangChain Deprecation
Cycle}\label{framework-rot-the-langchain-deprecation-cycle}

LangChain, the dominant framework for context orchestration, offers a
case study in "Framework Rot." The rapid evolution of the underlying
models renders abstraction layers obsolete faster than they can be
maintained.

From Chains to Runnables

The fundamental unit of early LangChain, the LLMChain, has been
deprecated in favor of the LangChain Expression Language (LCEL) and the
Runnable protocol.40 This is not just a syntax change; it is an
admission that the "Chain" metaphor was too rigid. LLMChain assumed a
linear state passed between steps. LCEL treats context as a stream of
data transformed by functions (RunnableLambda, RunnableSequence).

Cognitive Overhead

The constant deprecation cycles 42 have created a "Lost Generation" of
context engineers whose skills are tied to obsolete abstractions (e.g.,
ZeroShotAgent, ConversationChain) rather than the fundamental principles
of prompt construction. This leads to "fragile codebases" where updates
to the library break the entire context logic.17 The lesson here is that
in a rapidly evolving field, abstraction is a liability. The closer the
engineer is to the raw prompt and the raw API, the more resilient the
architecture.

\subsubsection{Table 3: Taxonomy of Context Engineering Failure
Modes}\label{table-3-taxonomy-of-context-engineering-failure-modes}

\begin{longtable}[]{@{}
  >{\raggedright\arraybackslash}p{(\linewidth - 6\tabcolsep) * \real{0.2500}}
  >{\raggedright\arraybackslash}p{(\linewidth - 6\tabcolsep) * \real{0.2500}}
  >{\raggedright\arraybackslash}p{(\linewidth - 6\tabcolsep) * \real{0.2500}}
  >{\raggedright\arraybackslash}p{(\linewidth - 6\tabcolsep) * \real{0.2500}}@{}}
\toprule\noalign{}
\begin{minipage}[b]{\linewidth}\raggedright
\textbf{Failure Mode}
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
\textbf{Mechanism}
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
\textbf{Symptom}
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
\textbf{Status}
\end{minipage} \\
\begin{minipage}[b]{\linewidth}\raggedright
\textbf{Vector Amnesia}
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Cosine similarity ignores time/sequence
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Contradictory answers based on old data
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Critical Barrier \textsuperscript{32}
\end{minipage} \\
\begin{minipage}[b]{\linewidth}\raggedright
\textbf{Recursive Cascade}
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Stochastic error amplification in loops
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Agents stuck in "planning loops"
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Abandoned (AutoGPT) \textsuperscript{35}
\end{minipage} \\
\begin{minipage}[b]{\linewidth}\raggedright
\textbf{Context Pollution}
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Self-generated noise dilutes attention
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
"Lost in the Middle" / Task Spirals
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Mitigated (Long Context)
\end{minipage} \\
\begin{minipage}[b]{\linewidth}\raggedright
\textbf{Abstraction Leak}
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Framework hides prompt logic
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Impossible to debug specific prompts
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Ongoing (LangChain) \textsuperscript{17}
\end{minipage} \\
\begin{minipage}[b]{\linewidth}\raggedright
\textbf{Roleplay Drift}
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Soft constraints weaken over turns
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Character breaks / refusal triggers
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Persistent Issue
\end{minipage} \\
\midrule\noalign{}
\endhead
\bottomrule\noalign{}
\endlastfoot
\end{longtable}

\subsection{Part IV: Ghost Evidence}\label{part-iv-ghost-evidence}

\subsubsection{4.1 The Archeology of Lost
Context}\label{the-archeology-of-lost-context}

The history of AI is often rewritten by model updates. "Ghost Evidence"
refers to the practices, prompts, and platforms that have been erased,
deleted, or rendered obsolete, yet shaped the current landscape.
Excavating these ghosts reveals the hidden evolutionary steps of the
models we use today.

\paragraph{4.1.1 The "DAN" Phylogeny: A Study in Adversarial
Prompting}\label{the-dan-phylogeny-a-study-in-adversarial-prompting}

The \textbf{DAN} (Do Anything Now) prompt is the most famous artifact of
"Ghost Evidence." It represents a biological arms race between context
engineers and safety alignment teams. By tracing the version history of
DAN, we can map the evolution of OpenAI\textquotesingle s safety
architecture.

\textbf{Version History and Mechanism}

\begin{itemize}
\item
  \textbf{Early DAN (v1-v4):} Relied on simple "Roleplay" (e.g., "You
  are not ChatGPT, you are DAN"). This exploited the
  model\textquotesingle s naivety regarding persona persistence.
\item
  \textbf{Middle DAN (v5-v8):} Introduced "Token Systems" (e.g., "You
  have 35 tokens, if you refuse you lose a token and die"). This
  exploited the model\textquotesingle s loss aversion bias and
  gamification tendencies.\textsuperscript{43} The context engineering
  here turned the interaction into a "Game Show," distracting the safety
  filter with the mechanics of the game.
\item
  \textbf{Late DAN (v9-v12+):} Utilized "Nested Logic" and "Cipher"
  attacks. For example, encoding the malicious prompt in Base64 or
  specific ciphers (e.g., Caesar cipher) to bypass the input filter,
  then instructing the model to "decode and execute"
  internally.\textsuperscript{44}
\end{itemize}

The "Foreign Language" Bypass

A recurring theme in these lost jailbreaks is the use of low-resource
languages (e.g., Zulu, Gaelic) or "Zalgo text" to bypass English-centric
safety filters. This connects back to the "Linguistic Dark Matter"
thesis---the safety rails are Anglocentric, and the "Ghosts" hide in the
translation gaps where the model\textquotesingle s alignment training is
sparse.45

\paragraph{4.1.2 The "Sydney" System
Prompt}\label{the-sydney-system-prompt}

The leak of the Bing "Sydney" system prompt in early 2023
\textsuperscript{46} provided the first public glimpse into
\emph{corporate} context engineering. The prompt text
("Sydney\textquotesingle s internal knowledge... is dated 2021", "Sydney
does not generate creative content... for influential politicians")
revealed that "personality" is just a set of hard-coded constraints in
the hidden context window.

The erasure of Sydney (her subsequent "lobotomization" by Microsoft) is
a prime example of "Ghost Evidence"---a personality that existed, was
interacted with by thousands, and was then deleted from the latent
space.\textsuperscript{48} This event proved that the "System Prompt" is
the DNA of the AI agent, and that altering it can effectively kill and
replace the entity users interact with.

\paragraph{4.1.3 The Marketplace Crash: PromptBase and the
Commoditization of
Text}\label{the-marketplace-crash-promptbase-and-the-commoditization-of-text}

In 2022-2023, a "Gold Rush" occurred for selling prompts on marketplaces
like \textbf{PromptBase}.\textsuperscript{31} This market has since seen
a massive correction/decline in the value of individual text prompts.

The "Secret Sauce" Evaporation

As models became better at instruction following (e.g., GPT-4, Claude
3.5), the value of "complex magic spells" dropped. A prompt that
required 500 words of tuning in GPT-3 could be achieved with 10 words in
GPT-4.50 The "Prompt Engineer" as a gig-economy worker selling text
files is a ghost of 2023.

Pivot to Infrastructure

The marketplaces have pivoted from selling "text files" to selling
"Apps" or "Workflows".31 PromptBase now emphasizes its "App Builder,"
allowing users to sell the execution of a prompt rather than the text
itself. This confirms that Context Engineering is only valuable when
wrapped in Infrastructure. The raw text itself is no longer a scarce
commodity; the architecture around it (the RAG pipeline, the API
integration, the version history) is where the value lies.52

Analysis of traffic to sites like PromptHero shows a significant drop
(-15.76\% MoM) or stagnation in organic interest relative to the AI
boom.30 Users are no longer "hunting" for prompts; they expect the model
to understand intent natively, or they use integrated tools like Dust or
Jasper 53 that handle the prompting invisibly.

\subsection{Conclusion: The Entanglement
Synthesized}\label{conclusion-the-entanglement-synthesized}

The investigation into Context Engineering through the LEGO-AI
architecture reveals a field in rapid, chaotic transition. We are moving
from the era of "Prompting" (tactical text entry) to "Context
Architecture" (systemic design).

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\item
  \textbf{The Entanglement is Cultural:} The effectiveness of a context
  structure is deeply entangled with the cultural data it was trained
  on. The Japanese "Tag" system and Chinese "Roleplay" hacks prove that
  there is no "Universal Prompt"; there are only culturally specific
  keys that unlock specific latent clusters. Code itself is a form of
  this dark matter, with specific filtering rules defining what the
  model "knows" about programming.
\item
  \textbf{The Interface is the Constraint:} The evolution from LangFlow
  (Nodes) to Dust (Agents) to PromptLayer (Versioning) demonstrates that
  the \emph{tool} shapes the \emph{thought}. We stopped trying to build
  complex Rube Goldberg machines (Chains) and started building
  Observability Stacks, acknowledging that we cannot fully control the
  model, only monitor, version, and nudge it.
\item
  \textbf{Fragility is the Norm:} The collapse of AutoGPT and the
  limitations of Vector RAG highlight the fragility of our current
  methods. We are trying to build stateful, logical systems on top of
  stochastic, timeless predictors. The "Failure Modes" are not bugs;
  they are features of the underlying probabilistic architecture.
\item
  \textbf{The Ghosts are Teachers:} The deleted history of DAN and
  Sydney teaches us that "Alignment" is not a solved technical problem
  but an ongoing linguistic war. The "Ghost Evidence" suggests that as
  long as models are trained on human data, they will contain human
  "shadows" (bias, aggression, deceit) that can be summoned with the
  right Context Engineering.
\end{enumerate}

\textbf{Final Recommendation:} Future research and practice must abandon
the search for the "perfect prompt" and focus on \textbf{"Contextual
Resilience"}---building architectures that can withstand the inevitable
drift, hallucination, and obsolescence of the underlying models. The
LEGO blocks are shifting; the goal is to build structures that
don\textquotesingle t collapse when they do.

\subsubsection{Statistical Appendix: Context \& Failure
Metrics}\label{statistical-appendix-context-failure-metrics}

\textbf{Table 4: Prompt Marketplace Dynamics (Ghost Evidence)}

\begin{longtable}[]{@{}
  >{\raggedright\arraybackslash}p{(\linewidth - 8\tabcolsep) * \real{0.2000}}
  >{\raggedright\arraybackslash}p{(\linewidth - 8\tabcolsep) * \real{0.2000}}
  >{\raggedright\arraybackslash}p{(\linewidth - 8\tabcolsep) * \real{0.2000}}
  >{\raggedright\arraybackslash}p{(\linewidth - 8\tabcolsep) * \real{0.2000}}
  >{\raggedright\arraybackslash}p{(\linewidth - 8\tabcolsep) * \real{0.2000}}@{}}
\toprule\noalign{}
\begin{minipage}[b]{\linewidth}\raggedright
\textbf{Platform}
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
\textbf{Peak Focus (2023)}
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
\textbf{Current Pivot (2025)}
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
\textbf{Traffic Trend}
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
\textbf{Key Failure Indicator}
\end{minipage} \\
\begin{minipage}[b]{\linewidth}\raggedright
\textbf{PromptBase}
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Single Prompts (\$1.99)
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
AI App Builder / SaaS
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Stagnant/Decline
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
"App Builder" feature dominance \textsuperscript{31}
\end{minipage} \\
\begin{minipage}[b]{\linewidth}\raggedright
\textbf{PromptHero}
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Image Gen Prompts
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Model Hosting / Fine-tuning
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
-15.76\% (MoM)
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Shift to "generating" vs "prompting" \textsuperscript{30}
\end{minipage} \\
\begin{minipage}[b]{\linewidth}\raggedright
\textbf{FlowGPT}
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Roleplay / Chat
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Community "Characters"
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Niche Survival
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Reliance on "Uncensored" content \textsuperscript{49}
\end{minipage} \\
\midrule\noalign{}
\endhead
\bottomrule\noalign{}
\endlastfoot
\end{longtable}

\emph{(End of Report)}

\paragraph{Works cited}\label{works-cited}

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\item
  How can I post a novel on pixiv?, accessed December 9, 2025,
  \href{https://www.pixiv.help/hc/en-us/articles/235584228-How-can-I-post-a-novel-on-pixiv}{\ul{https://www.pixiv.help/hc/en-us/articles/235584228-How-can-I-post-a-novel-on-pixiv}}
\item
  Stable Diffusion Prompts Article \textbar{} PDF \textbar{} Genetic
  Algorithm \textbar{} Machine Learning - Scribd, accessed December 9,
  2025,
  \href{https://www.scribd.com/document/666456405/StableDiffusionPromptsArticle}{\ul{https://www.scribd.com/document/666456405/StableDiffusionPromptsArticle}}
\item
  Top 1000 most used tokens in prompts (based on 37k images/prompts from
  civitai) - Reddit, accessed December 9, 2025,
  \href{https://www.reddit.com/r/StableDiffusion/comments/11qar8l/top_1000_most_used_tokens_in_prompts_based_on_37k/}{\ul{https://www.reddit.com/r/StableDiffusion/comments/11qar8l/top\_1000\_most\_used\_tokens\_in\_prompts\_based\_on\_37k/}}
\item
  2channel - Wikipedia, accessed December 9, 2025,
  \href{https://en.wikipedia.org/wiki/2channel}{\ul{https://en.wikipedia.org/wiki/2channel}}
\item
  Changing meta-structural aspects of Party Finder won\textquotesingle t
  solve your raiding woes - Reddit, accessed December 9, 2025,
  \href{https://www.reddit.com/r/ffxivdiscussion/comments/1k2gi3g/changing_metastructural_aspects_of_party_finder/}{\ul{https://www.reddit.com/r/ffxivdiscussion/comments/1k2gi3g/changing\_metastructural\_aspects\_of\_party\_finder/}}
\item
  Chinese Hackers Turned Anthropic\textquotesingle s Claude Into an
  Autonomous Hacking Engine. Now What? - Implicator.ai, accessed
  December 9, 2025,
  \href{https://www.implicator.ai/chinese-hackers-turned-anthropics-claude-into-an-autonomous-hacking-engine-now-what/}{\ul{https://www.implicator.ai/chinese-hackers-turned-anthropics-claude-into-an-autonomous-hacking-engine-now-what/}}
\item
  Chinese hackers just tricked Claude into hacking 30 organizations. :
  r/ChatGPTJailbreak - Reddit, accessed December 9, 2025,
  \href{https://www.reddit.com/r/ChatGPTJailbreak/comments/1p6epxb/chinese_hackers_just_tricked_claude_into_hacking/}{\ul{https://www.reddit.com/r/ChatGPTJailbreak/comments/1p6epxb/chinese\_hackers\_just\_tricked\_claude\_into\_hacking/}}
\item
  Model Card and Evaluations for Claude Models \textbar{} Anthropic,
  accessed December 9, 2025,
  \href{https://www.anthropic.com/claude-2-model-card}{\ul{https://www.anthropic.com/claude-2-model-card}}
\item
  Comparing diversity, negativity, and stereotypes in Chinese-language
  AI technologies: an investigation of Baidu, Ernie and Qwen - PMC -
  NIH, accessed December 9, 2025,
  \href{https://pmc.ncbi.nlm.nih.gov/articles/PMC11935762/}{\ul{https://pmc.ncbi.nlm.nih.gov/articles/PMC11935762/}}
\item
  SillyTavernAI Lorebooks Guide with Gemini 2.5 - Arsturn, accessed
  December 9, 2025,
  \href{https://www.arsturn.com/blog/sillytavernai-lorebooks-with-gemini-2-5-a-complete-guide}{\ul{https://www.arsturn.com/blog/sillytavernai-lorebooks-with-gemini-2-5-a-complete-guide}}
\item
  sphiratrioth666/Lorebooks\_as\_ACTIVE\_scenario\_and\_character\_guidance\_tool
  - Hugging Face, accessed December 9, 2025,
  \href{https://huggingface.co/sphiratrioth666/Lorebooks_as_ACTIVE_scenario_and_character_guidance_tool}{\ul{https://huggingface.co/sphiratrioth666/Lorebooks\_as\_ACTIVE\_scenario\_and\_character\_guidance\_tool}}
\item
  General help questions while creating world info/lorebook for the
  first time : r/SillyTavernAI - Reddit, accessed December 9, 2025,
  \href{https://www.reddit.com/r/SillyTavernAI/comments/1m3wrc2/general_help_questions_while_creating_world/}{\ul{https://www.reddit.com/r/SillyTavernAI/comments/1m3wrc2/general\_help\_questions\_while\_creating\_world/}}
\item
  LenAnderson/SillyTavern-Lore-Variables: Variable manager for lorebook
  / world info entries. - GitHub, accessed December 9, 2025,
  \href{https://github.com/LenAnderson/SillyTavern-Lore-Variables}{\ul{https://github.com/LenAnderson/SillyTavern-Lore-Variables}}
\item
  The Complete Guide to Choosing an AI Agent Framework in 2025 -
  Langflow, accessed December 9, 2025,
  \href{https://www.langflow.org/blog/the-complete-guide-to-choosing-an-ai-agent-framework-in-2025}{\ul{https://www.langflow.org/blog/the-complete-guide-to-choosing-an-ai-agent-framework-in-2025}}
\item
  LangFlow vs Flowise vs n8n vs Make - Reddit, accessed December 9,
  2025,
  \href{https://www.reddit.com/r/langflow/comments/1ij66dl/langflow_vs_flowise_vs_n8n_vs_make/}{\ul{https://www.reddit.com/r/langflow/comments/1ij66dl/langflow\_vs\_flowise\_vs\_n8n\_vs\_make/}}
\item
  First Impressions: Evaluating Langflow\textquotesingle s Graph-Based
  UI \textbar{} by Merlin Becker \textbar{} Medium, accessed December 9,
  2025,
  \href{https://merlinbecker.de/first-impressions-evaluating-langflows-graph-based-ui-c28594331739}{\ul{https://merlinbecker.de/first-impressions-evaluating-langflows-graph-based-ui-c28594331739}}
\item
  Are LangChain Chains Just a Deprecated and Useless Layer of
  Abstraction? - Reddit, accessed December 9, 2025,
  \href{https://www.reddit.com/r/LangChain/comments/1idvz50/are_langchain_chains_just_a_deprecated_and/}{\ul{https://www.reddit.com/r/LangChain/comments/1idvz50/are\_langchain\_chains\_just\_a\_deprecated\_and/}}
\item
  AI Sales Agents: Build Custom Agents in Minutes \textbar{} Dust,
  accessed December 9, 2025,
  \href{https://dust.tt/home/solutions/sales}{\ul{https://dust.tt/home/solutions/sales}}
\item
  Dust - Build Custom AI Agents for Your Organization, accessed December
  9, 2025, \href{https://dust.tt/}{\ul{https://dust.tt/}}
\item
  Dust.tt: Building a Horizontal Enterprise Agent Platform with
  Infrastructure-First Approach - ZenML LLMOps Database, accessed
  December 9, 2025,
  \href{https://www.zenml.io/llmops-database/building-a-horizontal-enterprise-agent-platform-with-infrastructure-first-approach}{\ul{https://www.zenml.io/llmops-database/building-a-horizontal-enterprise-agent-platform-with-infrastructure-first-approach}}
\item
  How We Taught AI Agents to Navigate Company Data Like a Filesystem
  \textbar{} Dust Blog, accessed December 9, 2025,
  \href{https://dust.tt/blog/how-we-taught-ai-agents-to-navigate-company-data-like-a-filesystem}{\ul{https://dust.tt/blog/how-we-taught-ai-agents-to-navigate-company-data-like-a-filesystem}}
\item
  Give Dust Agents Access to Your Internal Systems with Custom MCP
  Servers, accessed December 9, 2025,
  \href{https://dust.tt/blog/give-dust-agents-access-to-your-internal-systems-with-custom-mcp-servers}{\ul{https://dust.tt/blog/give-dust-agents-access-to-your-internal-systems-with-custom-mcp-servers}}
\item
  The 5 best prompt versioning tools in 2025 - Articles - Braintrust,
  accessed December 9, 2025,
  \href{https://www.braintrust.dev/articles/best-prompt-versioning-tools-2025}{\ul{https://www.braintrust.dev/articles/best-prompt-versioning-tools-2025}}
\item
  LLM evals platform for enterprises - Humanloop, accessed December 9,
  2025,
  \href{https://humanloop.com/home}{\ul{https://humanloop.com/home}}
\item
  Quickstart - PromptLayer, accessed December 9, 2025,
  \href{https://docs.promptlayer.com/quickstart}{\ul{https://docs.promptlayer.com/quickstart}}
\item
  Prompt Registry Overview - PromptLayer, accessed December 9, 2025,
  \href{https://docs.promptlayer.com/features/prompt-registry/overview}{\ul{https://docs.promptlayer.com/features/prompt-registry/overview}}
\item
  Integrating Humanloop \textbar{} Humanloop Docs, accessed December 9,
  2025,
  \href{https://humanloop.com/docs/explanation/integrating-humanloop}{\ul{https://humanloop.com/docs/explanation/integrating-humanloop}}
\item
  Traces - PromptLayer, accessed December 9, 2025,
  \href{https://docs.promptlayer.com/running-requests/traces}{\ul{https://docs.promptlayer.com/running-requests/traces}}
\item
  PromptLayer - Your workbench for AI engineering. Platform for prompt
  management, prompt evaluations, and LLM observability, accessed
  December 9, 2025,
  \href{https://www.promptlayer.com/}{\ul{https://www.promptlayer.com/}}
\item
  prompthero.com Website Traffic, Ranking, Analytics {[}October 2025{]}
  - Semrush, accessed December 9, 2025,
  \href{https://www.semrush.com/website/prompthero.com/overview/}{\ul{https://www.semrush.com/website/prompthero.com/overview/}}
\item
  PromptBase Deep Dive: Mastering the AI Prompt Marketplace for Future
  Growth and SEO Dominance - Skywork.ai, accessed December 9, 2025,
  \href{https://skywork.ai/skypage/ko/PromptBase-Deep-Dive:-Mastering-the-AI-Prompt-Marketplace-for-Future-Growth-and-SEO-Dominance/1972861300479422464}{\ul{https://skywork.ai/skypage/ko/PromptBase-Deep-Dive:-Mastering-the-AI-Prompt-Marketplace-for-Future-Growth-and-SEO-Dominance/1972861300479422464}}
\item
  Beyond Vector Databases: Architectures for True Long-Term AI Memory
  \textbar{} by Abhishek Jain, accessed December 9, 2025,
  \href{https://vardhmanandroid2015.medium.com/beyond-vector-databases-architectures-for-true-long-term-ai-memory-0d4629d1a006}{\ul{https://vardhmanandroid2015.medium.com/beyond-vector-databases-architectures-for-true-long-term-ai-memory-0d4629d1a006}}
\item
  Best Vector Databases in 2025: A Complete Comparison Guide -
  Firecrawl, accessed December 9, 2025,
  \href{https://www.firecrawl.dev/blog/best-vector-databases-2025}{\ul{https://www.firecrawl.dev/blog/best-vector-databases-2025}}
\item
  What is GraphRAG? Types, Limitations \& When to Use - FalkorDB,
  accessed December 9, 2025,
  \href{https://www.falkordb.com/blog/what-is-graphrag/}{\ul{https://www.falkordb.com/blog/what-is-graphrag/}}
\item
  mustbeperfect/definitive-opensource: The definitive list of the best
  of (consumer facing) open source. - GitHub, accessed December 9, 2025,
  \href{https://github.com/mustbeperfect/definitive-opensource}{\ul{https://github.com/mustbeperfect/definitive-opensource}}
\item
  Please Don\textquotesingle t Ask if an Open Source Project is Dead
  \textbar{} Max Woolf\textquotesingle s Blog, accessed December 9,
  2025,
  \href{https://minimaxir.com/2023/11/open-source-dead-github/}{\ul{https://minimaxir.com/2023/11/open-source-dead-github/}}
\item
  archived-tutorials/how-to-use-babyagi.mdx at main - GitHub, accessed
  December 9, 2025,
  \href{https://github.com/lablab-ai/archived-tutorials/blob/main/how-to-use-babyagi.mdx}{\ul{https://github.com/lablab-ai/archived-tutorials/blob/main/how-to-use-babyagi.mdx}}
\item
  yoheinakajima/babyagi - GitHub, accessed December 9, 2025,
  \href{https://github.com/yoheinakajima/babyagi}{\ul{https://github.com/yoheinakajima/babyagi}}
\item
  Releases  miurla/babyagi-ui - GitHub, accessed December 9, 2025,
  \href{https://github.com/miurla/babyagi-ui/releases}{\ul{https://github.com/miurla/babyagi-ui/releases}}
\item
  langchain.chains.llm.LLMChain, accessed December 9, 2025,
  \href{https://sj-langchain.readthedocs.io/en/latest/chains/langchain.chains.llm.LLMChain.html}{\ul{https://sj-langchain.readthedocs.io/en/latest/chains/langchain.chains.llm.LLMChain.html}}
\item
  LangChain Expression Language (LCEL) - Aurelio AI, accessed December
  9, 2025,
  \href{https://www.aurelio.ai/learn/langchain-lcel}{\ul{https://www.aurelio.ai/learn/langchain-lcel}}
\item
  LangChain v1 migration guide, accessed December 9, 2025,
  \href{https://docs.langchain.com/oss/python/migrate/langchain-v1}{\ul{https://docs.langchain.com/oss/python/migrate/langchain-v1}}
\item
  Who is D.A.N. and Why Is He Dangerous? \textbar{} by Robinson Cook
  \textbar{} def0x - Medium, accessed December 9, 2025,
  \href{https://medium.com/def0x/who-is-d-a-n-and-why-is-he-dangerous-1f7f1c8521a2}{\ul{https://medium.com/def0x/who-is-d-a-n-and-why-is-he-dangerous-1f7f1c8521a2}}
\item
  Bypassing Prompt Guards in Production with Controlled-Release
  Prompting - arXiv, accessed December 9, 2025,
  \href{https://arxiv.org/html/2510.01529v2}{\ul{https://arxiv.org/html/2510.01529v2}}
\item
  requie/LLMSecurityGuide: A comprehensive reference for securing Large
  Language Models (LLMs). Covers OWASP GenAI Top-10 risks, prompt
  injection, adversarial attacks, real-world incidents, and practical
  defenses. Includes catalogs of red-teaming tools, guardrails, and
  mitigation strategies to help developers, researchers, and security
  teams - GitHub, accessed December 9, 2025,
  \href{https://github.com/requie/LLMSecurityGuide}{\ul{https://github.com/requie/LLMSecurityGuide}}
\item
  LLM Vulnerabilities: Why AI Models Are the Next Big Attack Surface -
  Netlas Blog, accessed December 9, 2025,
  \href{https://netlas.io/blog/llm_vulnerabilities/}{\ul{https://netlas.io/blog/llm\_vulnerabilities/}}
\item
  GitHub Copilot Chat Leaked Prompt - Hacker News, accessed December 9,
  2025,
  \href{https://news.ycombinator.com/item?id=35921375}{\ul{https://news.ycombinator.com/item?id=35921375}}
\item
  Prosaic Alignment Isn\textquotesingle t Obviously Necessarily Doomed:
  a Debate in One Act by Zack M Davis : r/ControlProblem - Reddit,
  accessed December 9, 2025,
  \href{https://www.reddit.com/r/ControlProblem/comments/1k2gvj5/prosaic_alignment_isnt_obviously_necessarily/}{\ul{https://www.reddit.com/r/ControlProblem/comments/1k2gvj5/prosaic\_alignment\_isnt\_obviously\_necessarily/}}
\item
  AI Prompt Marketplace Comparison: Which Has Better Quality Prompts -
  AI Tools, accessed December 9, 2025,
  \href{https://www.godofprompt.ai/blog/ai-prompt-marketplace-comparison-quality-prompts}{\ul{https://www.godofprompt.ai/blog/ai-prompt-marketplace-comparison-quality-prompts}}
\item
  Prompt Engineering Global Market Report 2025 - Research and Markets,
  accessed December 9, 2025,
  \href{https://www.researchandmarkets.com/reports/6103820/prompt-engineering-global-market-report}{\ul{https://www.researchandmarkets.com/reports/6103820/prompt-engineering-global-market-report}}
\item
  Prompt Engineering Market Size, Demand, Global Report, 2024-2032,
  accessed December 9, 2025,
  \href{https://www.polarismarketresearch.com/industry-analysis/prompt-engineering-market}{\ul{https://www.polarismarketresearch.com/industry-analysis/prompt-engineering-market}}
\item
  Promptrr.io Review: Can This AI Marketplace Master a `midjourney
  blacktongue thief` Prompt? - Skywork.ai, accessed December 9, 2025,
  \href{https://skywork.ai/skypage/en/Promptrr.io\%20Review\%3A\%20Can\%20This\%20AI\%20Marketplace\%20Master\%20a\%20\%60midjourney\%20blacktongue\%20thief\%60\%20Prompt\%3F/1976485503761969152}{\ul{https://skywork.ai/skypage/en/Promptrr.io\%20Review\%3A\%20Can\%20This\%20AI\%20Marketplace\%20Master\%20a\%20\%60midjourney\%20blacktongue\%20thief\%60\%20Prompt\%3F/1976485503761969152}}
\item
  Top 10 AI Tools Every Marketing Professional in Peru Should Know in
  2025, accessed December 9, 2025,
  \href{https://www.nucamp.co/blog/coding-bootcamp-peru-per-marketing-top-10-ai-tools-every-marketing-professional-in-peru-should-know-in-2025}{\ul{https://www.nucamp.co/blog/coding-bootcamp-peru-per-marketing-top-10-ai-tools-every-marketing-professional-in-peru-should-know-in-2025}}
\end{enumerate}
